Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-06-19 template.tex
updated calculations for convolution in time domain

\item The RLC damped oscillator impulse response and corresponding analytic signal are

@@

\item The goal is now to apply Eq. \ref{eq:awesome} by convolving $s_a(t)$ with $r_a(t)$.  The real part of $s_a(t)$ can be convolved with $r_a(t)$ in the time domain.  As in Eq. \ref{eq:sa_4}, real part of $s_a(t)$ is $s(t)$.  Since $r_a(t<0)=0$, the convolution is written

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = \int_0^{\infty} r_a(\tau) s(t-\tau) d\tau

@@

Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z_0 = \sqrt{2}\sigma_t(\gamma-2\pi jf_0)$. The convolution may be organized as follows

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = R_0 s(t) I + R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t^2)} \frac{dI}{dt} \label{eq:conv}

@@

with

@@

I(x,z_0) = \sqrt{2}\sigma_t \int_0^{\infty} e^{-y^2 + (2x-z_0)y} dy

@@

Let $b = x-z_0/2$. Completing the square in the exponent produces

@@

I(x,z_0) = \sqrt{2}\sigma_t e^{b^2} \int_0^{\infty} e^{-(y-b)^2} dy

@@

The integral may be cast as a complementary error function by substituting $u=y-b$ and letting $b=jz$:
I(x,z_0) = \sqrt{\frac{\pi}{2}}\sigma_t e^{-z^2}\erfc(-jz)
Thus, the integral is proportional to the \textit{Faddeeva function}, $w(z)$:
I(x,z_0) = \sqrt{\frac{\pi}{2}} \sigma_t w(z) \label{eq:fadd}
Substituting Eq. \ref{eq:fadd} into Eq. \ref{eq:conv}, and simplifying, produces

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = \sqrt{\frac{\pi}{2}}R_0 \sigma_t s(t) w(z) \\
-j\frac{\sqrt{\pi}}{2} R_0 E_0 \sigma_t^2 e^{-\frac{1}{2}(t/\sigma_t)^2} \frac{dw(z)}{dz} \label{eq:Re_result}

@@

\item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$, note that the imaginary part of Eq. \ref{eq:sa_4} contains $dD(x)/dx$, the derivative of the Dawson function.  To complete the convolution, the inverse Fourier transform of the product of the Fourier transforms of $r_a(t)$ and $\Im\lbrace s_a(t)\rbrace$ is calculated.  To complete this step, the Fourier transform of $dD(x)/dx$ is needed:
x &= t/(\sqrt{2}\sigma_t) \\
f' &= \sqrt{2} \sigma_t f \\
\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \int_{-\infty}^{\infty} \frac{dD(x)}{dx}e^{-2\pi jft} dt \\
\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= \sqrt{2}\sigma_t(2\pi jf') \int_{-\infty}^{\infty} D(x) e^{-2\pi jf'x} dx \\
\mathcal{F}\left\lbrace \frac{dD(x)}{dx}\right\rbrace &= 2\pi^2 \sigma_t^2 f e^{-\frac{1}{2}(f/\sigma_f)^2} \sgn(f)
Let $z_0 = (\gamma - 2\pi jf_0)$, so that the Fourier transform of $r_a$ is 
\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= R_0\int_{0}^{\infty} e^{-z_0 t} e^{-2\pi j ft} dt \\
\mathcal{F}\left\lbrace r_a(t)\right\rbrace &= \frac{R_0}{z_0+2\pi j f}
Let $z_1 = f_0 + j\gamma/(2\pi)$. Multiplying the Fourier transforms, and simplifying, yields

@@

\mathcal{F}\left\lbrace r_a(t) * \Im\left\lbrace s_a(t)\right\rbrace \right\rbrace = \\ -j \sqrt{2\pi} R_0 E_0 \sigma^3 \frac{f\sgn(f) e^{-\frac{1}{2}(f/\sigma_f)^2}}{f-z_1}

@@

The inverse Fourier transform now gives $r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace$:

@@

r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-j\sqrt{2\pi} R_0 E_0 \sigma_t^3 \int_{-\infty}^{\infty} \frac{f\sgn(f)e^{-\frac{1}{2}(f/\sigma_f)^2}e^{2\pi jft}}{f-z_1} df

@@

Let $y = f/(\sqrt{2}\sigma_f)$, $x=t/(\sqrt{2}\sigma_t)$, $\sgn(f) = \sgn(y)$, and $z_1 \to f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.  The inverse Fourier transform can be organized as:

@@

r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\frac{R_0E_0\sigma_t^3}{\sqrt{2\pi}}\frac{d}{dt}\int_{-\infty}^{\infty} \frac{\sgn(y) e^{-y^2+2jxy}}{y-z_1} dy

@@

Completing the square in the exponent, factoring a unit of $j$ from the exponent, and changing the derivative from $d/dt$ to $d/dx$ gives

@@

r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{-\infty}^{\infty} \frac{\sgn(y) e^{(x+jy)^2}}{y-z_1}dy

@@

Let $z = x+jy$, with $y = \Im(z)$.  In this substitution, $x$ is treated as a constant, so $dz = jy$.  Let $z_2 = x+j z_1$, while $z_1 = f_0/(\sqrt{2}\sigma_f) + j\gamma/(2\pi \sqrt{2} \sigma_f)$.  The result is

@@

r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}e^{-x^2} \int_{x-j\infty}^{x+j\infty} \frac{\sgn(\Im(z)) e^{z^2}}{y-z_2}dz \label{eq:cont_int}

@@

The integral may be finished by extending $z$ to the complex plane and using contour integration.  The location of the pole is in the first quadrant, unless $t = (\gamma \sigma_t)\sigma_t$.  In that case, $\Re(z_2)=0$, and the pole is located on the imaginary axis.  For typical values of $\sigma_t$ and $\gamma$, $t\approx 0.1$ ns. Since $r(t)=0$ if $t<0$, the location of $z_2$ is usually in the first quadrant.  Let the line integrals of the rectangular contour be: $I_1$, $(x,-jR) \to (x,jR)$, $I_2$, $(x,jR) \to (0,jR)$, $I_3$, $(0,jR) \to (0,-jR)$, and $I_4$, $(0,-jR) \to (x,-jR)$.  $I_2$ and $I_4$ are both proportional to $\exp(-R^2)$, so $I_2 \to 0$ and $I_4 \to 0$ when $R \to \infty$.  $I_1$ is the integral in Eq. \ref{eq:cont_int}.  Let $w = -y$, so that $I_3$ is
I_3 = -\int_0^{R} \frac{e^{-y^2}}{y-z_1} dy + \int_0^{R} \frac{e^{-w^2}}{w+z_1} dw
Integrals of the type in $I_3$ are known as \textit{Goodwin-Staton} functions, and are related to the other error functions.  The Goodwin-Staton function, $G(z_1)$, is odd, so $-G(-z_1) = G(z_1)$.  The result for $I_3$ is
I_3 = -G(-z_1) + G(z_1) = 2G(z_1)
The residue of the enclosed contour $I_C = I_1+I_2+I_3+I_4$ is $\exp(z_2^2)$.  With $I_2$, $I_3$, and $I_4$ completed, the solution for $I_1$ is
I_1 = 2\pi j e^{z_2^2} - 2G(z_1)
Inserting this result into Eq. \ref{eq:cont_int}, and simplifying, gives

@@

r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
-\frac{R_0E_0\sigma_t^2}{2\sqrt{\pi}}\frac{d}{dx}\left( 2\pi j e^{2 j x z_1 - z_1^2} - 2G(z_1) e^{-x^2} \right)

@@

Notice that $2\pi j x z_1 = 2\pi j f_0 t - \gamma t$.  Evaluating the derivative and simplifying gives the final result:
r_a(t) * \Im\left\lbrace s_a(t) \right\rbrace = \\
\sqrt{\pi}E_0 \sigma_t^2 z_1 e^{-z_1^2}r_a(t) + \sqrt{\frac{2}{\pi}} G(z_1) R_0 \sigma_t s(t) \label{eq:Im_result}

>>>>

\item Assume that a signal arrives in an RLC damped oscillator at $t=0$.  For $t\geq 0$, the impulse response and corresponding analytic signal are

@@

\item The goal is now to apply Eq. \ref{eq:awesome} by convolving $s_a(t)$ with $r_a(t)$.  The calculation may be split into two parts: $r_a(t) * \Re\lbrace s_a(t) \rbrace$, and $r_a(t) * \Im\lbrace s_a(t) \rbrace$.  Let $u(t)$ represent the Heaviside step function.  Starting with $r_a(t) * \Re\lbrace s_a(t) \rbrace$:
r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ R_0 e^{2\pi j f_0 t} e^{-2\pi\gamma t} u(t) * \left(-E_0 t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2}\right)
Let $x=t/(\sqrt{2}\sigma_t)$, $y=\tau/(\sqrt{2}\sigma_t)$, and $z = (2\pi j f_0 - 2\pi\gamma)\sqrt{2}\sigma_t$.  Changing variables while accounting for the relationship between $u(t)$, $x$, and $y$, gives
r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ -2R_0 E_0 \sigma_t^2 \int_{-\infty}^{x} e^{z(x-y)} y e^{-y^2} dy
Note that the units for the convolution of $r(t)$ and $s(t)$ correspond to $R_0 E_0 \sigma_t^2$.  Let $u = x-y$, so that $du = -dy$. The result is

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = 2R_0 E_0 \sigma_t^2\left(\frac{dI(x,z)}{dz}-xI(x,z)\right)

@@

where

@@

I(x,z) = \int_0^{\infty} e^{zu} e^{-(u-x)^2} du

@@

Let $b = x+\frac{1}{2} z$. Completing the square in the exponent and substituting $k = u-b$ gives
I(x,z) = e^{-x^2} e^{b^2} \int_{-b}^{\infty} e^{-k^2} dk \\ = \frac{\sqrt{\pi}}{2} e^{-x^2} e^{b^2} \erfc(-b)
Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function}.  The integral becomes

@@

I(x,z) = \frac{\sqrt{\pi}}{2} e^{-x^2} w(q)

@@

The chain rule is required to find $dI/dz$:

@@

\frac{dI}{dz} = \frac{dI}{dq}\frac{dq}{dz} = -\left(\frac{j}{2}\right)\frac{dI}{dq}

@@

The final result is

@@

r_a(t) * \Re\lbrace s_a(t) \rbrace = \\ -\sqrt{\pi} R_0 E_0 \sigma_t^2 \left(x e^{-x^2} w(q) + \left(\frac{j}{2}\right) e^{-x^2} \frac{dw(q)}{dq} \right) \label{eq:Re_result}

@@

\item Turning to the convolution of $r_a(t)$ with $\Im(s_a)$,

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \left(R_0 e^{2\pi j f_0 t} e^{-2\pi \gamma t} u(t)\right) * \left(\frac{2 E_0 \sigma_t^2}{\sqrt{\pi}}\frac{dD(t/\sqrt{2}\sigma_t)}{dt} \right)

@@

Note that $f'(t) * g(t) = f(t) * g'(t) = (f(t) * g(t))'$.  Thus,

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dt}\left(e^{2\pi j f_0 t}e^{-2\pi\gamma t} u(t) * D(t/\sqrt{2}\sigma_t) \right)

@@

Accounting for the step function in the convolution gives

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dt} \int_{-\infty}^{t} e^{(2\pi j f_0 - 2\pi\gamma)(t-\tau)}D(\tau/\sqrt{2}\sigma_t)d\tau

@@

Adopting the earlier definitions of $x$, $y$, and $z$ gives

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \frac{d}{dx} \int_{-\infty}^{x} e^{z(x-y)} D(y) dy

@@

Using the fundamental theorem of calculus, 

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + z\int_{-\infty}^{x} e^{z(x-y)} D(y) dy \right)

@@

Let $u = x-y$, so that $du = -dy$ and note that $D(x)$ is an odd function.  The substitution gives

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) - z\int_{0}^{\infty} e^{zu} D(u-x) du \right)

@@

The integral is the Laplace transform of the shifted Dawson function, evaluated at $-z$.
